LSOA domestic Electricty and Gas maps

### 2021-09-02 LSOA domestic Elec and Gas.Rmd
added IMD score checks

# check IMD decile is higher with higher deprivation
library(data.table)
dt <- as.data.table(Solent)
dt[, .(nLSOAs = .N,
       meanIMDScore = mean(IMDScore)),
   keyby = .(IMD_Decile)]

ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y = IMDScore, 
                   group = IMD_Decile,
                   colour = IMD_Decile)) +  
  geom_boxplot() +
  scale_color_continuous(name = "IMD Decile") + # rename the legend scale
  labs(x = "IMD Decile",
       y = "IMD Score")
```

NB: IMD Decile 10 has _LOWER_ IMD score!

>>>>

# check IMD decile is higher or lower with higher deprivation
ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y = IMDScore, 
                   group = IMD_Decile,
                   colour = IMD_Decile)) +  
  geom_boxplot() +
  scale_color_continuous(name = "IMD Decile") + # rename the legend scale
  labs(x = "IMD Decile",
       y = "IMD Score")
```

NB: IMD Decile 10 has _LOWER_ mean IMD score!
